### 2021-07-05 ch/4-structure.tex
More corrections

\chapter{Summary of contributions}\label{ch:content}
The following is a summary of the main contributions in this thesis.
All presented approaches deal with dataset bias that is closely linked to a special attribute $s$.
In terms of \citet{kamishima2012fairness}'s taxonomy (see section \secref{fair-classifiers}),
this can be described as tackling \emph{negative legacy} that is mediated by \emph{prejudice}.
Furthermore, the approaches all rely on some form of side information with allows us to overcome dataset bias.
This side information is always significantly easier to obtain than unbiased data.

@@

In order to construct the target labels,
we use side information about summary statistics for an balanced training set.
This allows us to target a specific balanced set, instead of just any balanced set.
In other words, rather than just enforcing \ac{DP}, the method gives control over the target rates \(P(\hat{y}=1|s)\).
These target rates are the only parameters of the model.
The target labels represent an uncertain estimate of labels corresponding to a balanced dataset.
Via the sum rule of probabilities, it is possible to express the model likelihood in terms of these target labels,
such that maximising the likelihood corresponds to improving the prediction of the target labels
instead of the given (biased) training labels.

\section{Overcoming severe sampling bias with a representative set}\label{sec:nifr}
In the setting from the previous paper \citep{kehrenberg2020tuning},
labels were untrustworthy because they had been flipped;
a phenomenon we referred to as \emph{label bias}.
However, flipping labels is not the only way that labels can become untrustworthy.
Another way is \emph{sampling bias}, which is the subject of \citet{kehrenberg2020nullsampling} and \citet{kehrenberg2020zeroshot} (\twochaprefs{ch:paper2}{ch:paper3}).

>>>>

\chapter{Summary of contributions}\label{ch:content}
The following is a summary of the main contributions in this thesis.
All presented approaches deal with dataset bias that is closely linked to a special attribute $s$.
In terms of \citet{kamishima2012fairness}'s taxonomy (see section \secref{fair-classifiers}),
this can be described as tackling \emph{negative legacy} that is mediated by \emph{prejudice}.
Furthermore, the approaches all rely on some form of side information which allows us to overcome dataset bias.
This side information is always significantly easier to obtain than unbiased data.

@@

In order to construct the target labels,
we use side information about summary statistics for a balanced training set.
This allows us to target a specific balanced set, instead of just any balanced set.
In other words, rather than just enforcing \ac{DP}, the method gives control over the target rates \(P(\hat{y}=1|s)\).
These target rates are the only parameters of the model.
The target labels represent an uncertain estimate of labels corresponding to a balanced dataset.
Via the sum rule of probabilities, it is possible to express the model likelihood in terms of these target labels,
such that maximising the likelihood corresponds to improving the prediction of the target labels
instead of the given (biased) training labels.

\section{Overcoming severe sampling bias with a representative set}\label{sec:nifr}
In the setting from the above paper \citep{kehrenberg2020tuning},
labels were untrustworthy because they had been flipped;
a phenomenon we referred to as \emph{label bias}.
However, flipping labels is not the only way that labels can become untrustworthy.
Another way is \emph{sampling bias}, which is the subject of \citet{kehrenberg2020nullsampling} and \citet{kehrenberg2020zeroshot} (\twochaprefs{ch:paper2}{ch:paper3}).
